Manuscript_Github_Pchabaudi_compBerghei

### 2022-08-08 chapter4_results_chabaudi24h/Thesis_Github_Pchabaudi_compBerghei.Rmd
Improve graph labels

ggplot(filter(chab_tpm_subfam_norm.df.long, 
              !subfam == 'ancestral (n = 1)'), 
       aes(x = factor(name,
                      levels = ordering(name, 
                                        order_vector = c(times_stages_table$time, 'sch.culture'))),
           y = norm_tpm,
           fill = subfam)) +
  geom_col(position = "stack") +
  facet_wrap(~transmission, scales = "free_x") +
  scale_fill_manual(values = clade_col_num[!names(clade_col_num) == 'ancestral (n = 1)']) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 90))

@@

```{r berghei_subfam}
berg_tpm_subfam.df.long <- berghei_tpm[,
                                       c('Geneid',
                                         str_subset(colnames(berghei_tpm), 
                                                    pattern = 'Asex'))] %>% 
  filter(Geneid %in% bir_id) %>% 
  melt(id.vars = 'Geneid', variable.name = 'sample', value.name = 'tpm') %>% 
  mutate(subfam = bir_clade$subfam_num[match(Geneid, bir_clade$Geneid)],
         experiment = str_extract(sample, pattern = '^E[[:digit:]]{2}'),
         stage = str_extract(sample, 'Asex.+(?=_[[:digit:]])'),
         name = str_extract(sample, 'Asex.+'))

ggplot(berg_tpm_subfam.df.long, 
       aes(x = factor(name,
                      levels = ordering(name,
                                        order_vector = c('Ring','Troph','Schiz','Mixed'))),
           y = tpm,
           fill = subfam)) +
  geom_col(position = "fill") +
  scale_fill_manual(values = bir_clade_col_num) +
  facet_wrap(~experiment, scales = "free_x")+
  theme_classic()+
  theme(axis.text.x = element_text(angle = 90))
```

@@

ggplot(filter(berg_tpm_subfam_norm.df.long, 
              !subfam == 'ancestral (n = 1)'), 
       aes(x = factor(name,
                      levels = ordering(name, 
                                        order_vector = c('Ring','Troph','Schiz','Mixed'))),
           y = norm_tpm,
           fill = subfam)) +
  geom_col(position = "stack") +
  facet_wrap(~experiment, scales = "free_x") +
  scale_fill_manual(values = bir_clade_col_num[!names(bir_clade_col_num) %in% c('ancestral (n = 1)',
                                                                                'S6 (n = 1)')]) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 90))
```

>>>>

ggplot(filter(chab_tpm_subfam_norm.df.long, 
              !subfam == 'ancestral (n = 1)'), 
       aes(x = factor(name,
                      levels = ordering(name, 
                                        order_vector = c(times_stages_table$time, 'sch.culture'))),
           y = norm_tpm,
           fill = subfam)) +
  geom_col(position = "fill") +
    xlab('stages') +
  ylab('TPM per gene') +
  facet_wrap(~transmission, scales = "free_x") +
  scale_fill_manual(values = clade_col_num[!names(clade_col_num) == 'ancestral (n = 1)']) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 90))

@@

```{r berghei_subfam}
berg_tpm_subfam.df.long <- berghei_tpm[,
                                       c('Geneid',
                                         str_subset(colnames(berghei_tpm), 
                                                    pattern = 'Asex'))] %>% 
  filter(Geneid %in% bir_id) %>% 
  melt(id.vars = 'Geneid', variable.name = 'sample', value.name = 'tpm') %>% 
  mutate(subfam = bir_clade$subfam_num[match(Geneid, bir_clade$Geneid)],
         experiment = str_extract(sample, pattern = '^E[[:digit:]]{2}'),
         stage = str_extract(sample, 'Asex.+(?=_[[:digit:]])'),
         name = str_extract(sample, '(?<=Asex\\.).+'))

ggplot(berg_tpm_subfam.df.long, 
       aes(x = factor(name,
                      levels = ordering(name,
                                        order_vector = c('Ring','Troph','Schiz','Mixed'))),
           y = tpm,
           fill = subfam)) +
  geom_col(position = "fill") +
  xlab('stages') +
  scale_fill_manual(values = bir_clade_col_num) +
  facet_wrap(~experiment, scales = "free_x")+
  theme_classic()+
  theme(axis.text.x = element_text(angle = 90))
```

@@

ggplot(filter(berg_tpm_subfam_norm.df.long, 
              !subfam == 'ancestral (n = 1)'), 
       aes(x = factor(name,
                      levels = ordering(name, 
                                        order_vector = c('Ring','Troph','Schiz','Mixed'))),
           y = norm_tpm,
           fill = subfam)) +
  geom_col(position = "fill") +
  xlab('stages') +
  ylab('TPM per gene') +
  facet_wrap(~experiment, scales = "free_x") +
  scale_fill_manual(values = bir_clade_col_num[!names(bir_clade_col_num) %in% c('ancestral (n = 1)',
                                                                                'S6 (n = 1)')]) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 90))
```
